### 2019-09-15 2019_neurips_vigil/intro.tex
intro

\subsection{Contributions}
This work have attempted to address the issues mentioned above and propose a new model that can dynamically process video input frame-by-frame, reason over images and remember the salient concepts to answer questions.  We have tested this model on the COG dataset \cite{yang2018dataset} and compared to the baseline results.  Our results indicate that the model is capable of:
%\begin{itemize}
%\item \textbf{Time aspect}:
\begin{itemize}
\item Learning the temporal association - grounding the time-related words with meaning
%\item Learning the concept of time
%\item time context being by-product of gates
%\end{itemize}

>>>>

\subsection{Contributions}
This work introduces a new model that can dynamically process video input frame-by-frame, reason over images and remember the salient concepts to answer questions.  Our results based on the COG dataset \cite{yang2018dataset} indicate that the model is capable of:
%\begin{itemize}
%\item \textbf{Time aspect}:
\begin{itemize}
\item Learning the temporal association - grounding the time-related words with meaning
%\item Learning the concept of time
%\item time context being by-product of gates
%\end{itemize}
